---
title: "My R Markdown Primer"
author: "Jesse S"
date: "2025-11-11"
output: html_document
---

### Introduction

R Markdown is a file format for making dynamic documents with R. R Markdown allows you to combine code, output, and narrative text in a single document.

### Narrative Paragraph

This document is an example of R Markdown's capabilities. In this document We will populate a LaTeX math expression, load a dataset, perform a simple analysis, and display a plot. The biggest benefit of R Markdown is that if the data changes, we can knit the document again to update all the results automatically.

LaTeX math expression:
$$
\alpha + \beta = \gamma
$$

### Executables

```{r}
library(ggplot2)

```

```{r}
data(iris)

summary(iris)

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Iris Sepal Length vs. Petal Length",
       x = "Sepal Length (cm)",
       y = "Petal Length (cm)")
```

R Markdown is significantly more efficient than creating a plain report. The ability to embed executable code directly within the narrative ensures that the figures and statistics are reproducible and always up-to-date. This integrated workflow prevents copy-paste errors and streamlines the process of creating data-driven reports.